Gastro-intestinal transmission and colonisation of _Clostridioides difficile_ and antimicrobial-resistant bacteria in healthcare settings -- calibration of an agent-based model

### 2025-10-07 paper/paper.qmd
paper updates

```{r}
stochastic_sd <- read_csv("../out/sd_stochastic experiment-table.csv", skip = 6)
```

```{r}
Rcpp::sourceCpp("../models/sd_stochastic.cpp")
```

```{r}
set.seed(42)
randomLHS_sd <- randomLHS(1000000, 8)
sd_param_grid <- data.frame(init_population = rep(610, 1000),
                            A = 68,
                            r = qunif(randomLHS_sd[, 3], 0.001, 0.01),
                            baseline_beta = qunif(randomLHS_sd[, 4], 0.0001, 0.01),
                            baseline_p = qunif(randomLHS_sd[, 5], 0.001, 0.1),
                            outbreak_beta = qunif(randomLHS_sd[, 6], 0.0001, 0.01),
                            outbreak_p = qunif(randomLHS_sd[, 7], 0.001, 0.1),
                            outbreak_start = rep(1042, 1000),
                            outbreak_end = rep(1234, 1000),
                            n_days = rep(2585, 1000))

@@

```
```{r fig-abc-sd-posteriors, include=TRUE}
#| echo: false
#| fig.cap: "Posterior distributions of parameters obtained from approximate Bayesian computation using summary statistics generated from the stochastic deterministic model. The red line shows the prior distribution; the blue line shows the posterior distribution."
```

@@

```{r fig-abc-sd-posterior-predictive-check, include=TRUE}
#| echo: false
#| fig.cap: "Posterior predictive check of the stochastic deterministic model. Simulations were generated by sampling with replacement from the posterior parameter distributions after approximate Bayesian computation. Each simulation was run using different random number generators. The red line shows the true observed infection rates. The black solid line shows the median simulated rates; the dashed lines show the 25^th^ and 75^th^ quantiles."

posterior_predictive_sim_sd_rates %>% 
  pivot_wider(names_from = date_sim, values_from = rate) %>% 
  pivot_longer(cols = !c(`random-seed`, `param_row`), names_to = "date_sim", values_to = "rate") %>% 
  mutate(date_sim = ymd(date_sim)) %>% 
  group_by(date_sim) %>%
  summarise(m = median(rate),
            q_high = quantile(rate, 0.75),
            q_low = quantile(rate, 0.25),
            .groups = "keep") %>%
  ggplot() +
  geom_line(aes(x = date_sim, y = m)) +
  geom_line(aes(x = date_sim, y = q_high), linetype='dashed') +
  geom_line(aes(x = date_sim, y = q_low), linetype='dashed') + 
  geom_line(data = long_observed_ss, aes(x = x, y = rates), color = "red") +
  guides(color="none") +
  xlab("Date") + ylab("Rate (cases per 1000 patient days)")

>>>>

```{r load-stochastic-sd-model, include=FALSE}
Rcpp::sourceCpp("../models/sd_stochastic.cpp")
```

```{r run-stochastic-sd-model, include=FALSE, cache=TRUE}
set.seed(42)
randomLHS_sd <- randomLHS(1000000, 8)
sd_param_grid <- data.frame(init_population = rep(610, 1000),
                            A = 68,
                            r = qunif(randomLHS_sd[, 3], 0.001, 0.01),
                            baseline_beta = qunif(randomLHS_sd[, 4], 0.0001, 0.01),
                            baseline_p = qunif(randomLHS_sd[, 5], 0.001, 0.1),
                            outbreak_beta = qunif(randomLHS_sd[, 6], 0.0001, 0.01),
                            outbreak_p = qunif(randomLHS_sd[, 7], 0.001, 0.1),
                            outbreak_start = rep(1042, 1000),
                            outbreak_end = rep(1234, 1000),
                            n_days = rep(2585, 1000))

@@

```{r fig-abc-sd-posteriors, include=TRUE}
#| echo: false
#| fig.cap: "Posterior distributions of parameters obtained from approximate Bayesian computation using summary statistics generated from the stochastic deterministic model. The red line shows the prior distribution; the blue line shows the posterior distribution."
```

@@

```{r fig-abc-sd-posterior-predictive-check, include=FALSE, eval=FALSE}
#| echo: false
#| fig.cap: "Posterior predictive check of the stochastic deterministic model. Simulations were generated by sampling with replacement from the posterior parameter distributions after approximate Bayesian computation. Each simulation was run using different random number generators. The red line shows the true observed infection rates. The black solid line shows the median simulated rates; the dashed lines show the 25^th^ and 75^th^ quantiles."
